Capstone Movielens Report

### 2025-02-06 reports/capstone-movielens-report.Rmd

```{r setup, include=TRUE, echo = FALSE}

knitr::opts_chunk$set(echo = TRUE)
```

@@

@@

* **edx:** we use it to develop and train our algorithms;
* **final_holdout_test:** According to the course instructions, we use it exclusively to evaluate the _**RMSE**_ of our final algorithm.

```{r cars}
summary(cars)
```

## Methods / Analysis

>>>>

```{r setup, include=TRUE, echo = FALSE}
if(!require(pak)) install.packages("pak")
knitr::opts_chunk$set(echo = TRUE)
```

@@

``` {r , echo = FALSE}
```

@@

* **edx:** we use it to develop and train our algorithms;
* **final_holdout_test:**  according to the course requirements, we use it exclusively to evaluate the _**RMSE**_ of our final algorithm.

For this purpose the following package has been developed by the author: `edx.capstone.movielens.data`. The source code of the package is available [on GitHub](https://github.com/AzKurban-edX-DS/edx.capstone.movielens.data)[@edx_capstone_movielens_data].

Let us install the development version of this package from the GitHub repository and attach the correspondent library to the global environment:
```{r }
if(!require(edx.capstone.movielens.data)) pak::pak("AzKurban-edX-DS/edx.capstone.movielens.data")

library(edx.capstone.movielens.data)
edx <- edx.capstone.movielens.data::edx
final_holdout_test <- edx.capstone.movielens.data::final_holdout_test

summary(edx)
summary(final_holdout_test)
```

``` {r edx, echo = FALSE}
```
## Methods / Analysis
